Temporal dataflow graphs and their application to generative music

### 2017-03-21 article-icmc2017.tex
save work

    Throughout this paper, we will use the execution trace in fig.~\ref{fig.simple} as running example. 
    \begin{figure}
        \centering
        \begin{tikzpicture}[scale=0.5]
        \draw[line width=2pt] (0, 0) -- (0, 2) -- (5, 2) -- (5, 0) -- (0, 0);
        \draw[line width=2pt] (0 + 3, 0 - 2.5) -- (0 + 3, 2 - 2.5) -- (5 + 3, 2 - 2.5) -- (5 + 3, 0 - 2.5) -- (0 + 3, 0 - 2.5);

@@

@@

    The delayed execution has be specifieds explicitely for the tokens to be bufferised.

@@

    \section{Default behaviours for orders}
    The temporal graph allows to bypass a bit of cable writing.

    \subsection{Manual}
    The user explicitely draws a cable.

    \subsection{Hierarchical}
    We follow the hierarchical organization of the temporal graph.

    \subsection{Temporal glutton}
    If no order is given for the glutton case, the temporal order in which objects are executed
    will become the order of chaining in the call graph.

@@

    \begin{figure}
        \centering
        \begin{tikzpicture}[scale=0.5]
        \draw[line width=2pt] (0 + 3, 0) -- (0 + 3, 2) -- (5 + 3, 2) -- (5 + 3, 0) -- (0 + 3, 0);
        \draw[line width=2pt] (0, 0 - 2.5) -- (0, 2 - 2.5) -- (5, 2 - 2.5) -- (5, 0 - 2.5) -- (0, 0 - 2.5);

        \node (f1) at (5.5, 1) {\large $f_1$} ;
        \node (f2) at (2.5, -1.5) {\large $f_2$} ;
        \end{tikzpicture}
        \caption{A possible trace of execution for two processes}
        \label{fig.simple-reversed}
    \end{figure}

	\section{Evaluation}
    We present here the evaluation algorithm that operates at each tick.

>>>>

    Throughout this paper, we will use the execution traces in fig.~\ref{fig.simple} and fig.~\ref{fig.simple-reversed} as running example. 
    \begin{figure}
        \centering
        \begin{tikzpicture}[scale=0.5]
        \draw[line width=2pt] (0, 0) -- (0, 2) -- (5, 2) -- (5, 0) -- (0, 0);
        \draw[line width=2pt] (0 + 3, 0 - 2.5) -- (0 + 3, 2 - 2.5) -- (5 + 3, 2 - 2.5) -- (5 + 3, 0 - 2.5) -- (0 + 3, 0 - 2.5);

@@

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}[scale=0.5]
        \draw[line width=2pt] (0 + 3, 0) -- (0 + 3, 2) -- (5 + 3, 2) -- (5 + 3, 0) -- (0 + 3, 0);
        \draw[line width=2pt] (0, 0 - 2.5) -- (0, 2 - 2.5) -- (5, 2 - 2.5) -- (5, 0 - 2.5) -- (0, 0 - 2.5);

        \node (f1) at (5.5, 1) {\large $f_1$} ;
        \node (f2) at (2.5, -1.5) {\large $f_2$} ;
        \end{tikzpicture}
        \caption{Another trace of execution with the same processes}
        \label{fig.simple-reversed}
    \end{figure}

@@

    The delayed execution has be specified explicitely for the tokens to be bufferised.

    If we have a delay connection from $f_1$ to $f_2$, the first call to $f_2$ will use the first value that was produced by $f_1$, and nothing before.

@@

    \section{Default behaviours for orders}
    We study here the various behaviours possible to handle the dependency between nodes of the graph. 
    We can for instance leverage information provided in the temporal graph to connect the nodes at runtime.

    \subsection{Manual ordering}
    The user explicitely draws a cable between two ports.

    \subsection{Hierarchical}
    We follow the hierarchical organization of the temporal graph~: each time constraint has an ordered list of processes, and each time constraint is itself ordered in the scenario. This gives an order between processes.

    \subsection{Temporal}
    If no order is given, the temporal order in which objects are executed
    will become the order of chaining in the call graph.

@@

	\section{Evaluation algorithm}
    We present here the evaluation algorithm that operates at each tick.
